My title

### 2022-02-28 outputs/paper/paper.Rmd
country intro & data description

@@

We started our analysis by using R [@r], dplyr[@dplyr], tidyverse[@tidyverse]. Graphs are generated using ggpubr[@ggpubr] and ggplot2[@ggplot2].
```{r, include=FALSE}
#importing the Birth Rate 1950-2022 of the least affected countries: China, Japan, and the United States from https://www.macrotrends.net/countries/USA/united-states/birth-rate
#Then modify the 'date' variable of each into Date format for graphs by using as.Date
china_data <- read_csv(here::here("inputs/data/china-population-2022-02-25.csv"))
china_data$date <- as.Date(china_data$date)
str(china_data)

>>>>

As mentioned by @cite_original, the basic approach to many economic problem is maximizing utility. This approach recognized that children bring people utility but also with associated costs including time and money. This approach to modeling the decision to have a child leads to standard predictions of price and income effects. Direct consideration of costs could be like housing and medical care. Other times the price effect is indirect, like the opportunity cost of a woman’s time. Holding prices and quality constant, an increase in income will lead people to choose to have more children. This positive relationship between income and births may come as a surprise to some readers, given the negative relationship between birth rates and income or per capita GDP observed over time and place[@cite_original]. However, this is enough for us to consider whether the birth rates are world-wide affected in the same negative direction after the Great Recession.

@@

We started our analysis by using R [@r], dplyr[@dplyr], tidyverse[@tidyverse]. Graphs are generated using ggpubr[@ggpubr] and ggplot2[@ggplot2].

We generated data from U.S. Birth Rate 1950-2022[@birthrate]. We selected top 3 countries that are affected most and least by the Great Recession according to rankings determined by comparing currency devaluations, equity market declines, and rising sovereign bond spreads These measures tend to track developments in the real economy during times of economic crisis when financial strain handicaps consumption, investment, and in many cases government spending, which limits GDP and employment growth[@rank].
```{r, include=FALSE}
#importing the Birth Rate 1950-2022 of the least affected countries: China, Japan, and the United States from https://www.macrotrends.net/countries/USA/united-states/birth-rate
#Then modify the 'date' variable of each into Date format for graphs by using as.Date
china_data <- read_csv(here::here("inputs/data/china-population-2022-02-25.csv"))
china_data$date <- as.Date(china_data$date)
str(china_data)
